%======================问题介绍==================
\section{Restatement of the problems}
\subsection{Background}
\par Taxi is an important way for passengers to go to the destination after getting off the plane. Passengers who want to take a taxi will go to the loading area for queuing, and then take a taxi. The airport's managers will allocate the number of passengers and taxis allowed. Domestic taxis often need to make decisions after delivering guests to the airport:

(A) go to the "car storage pool" and wait in line to take passengers and then return to the city. There is a time cost of queuing.

(B) return to the urban area without load, save the cost of queuing time, but pay the cost of no-load, and lose the potential passenger source of the airport.

For how to make decisions, drivers often judge empirically by the number of flights and passengers arriving in a certain period of time. In the real scene, there are many determinate and non determinate factors that affect the choice of drivers.

\subsection{Tasks}
\par In this paper, the mathematical model is established and the following problems are solved:

(1) find out the factors that affect the driver's judgment, including taxi revenue, number of airport passengers, etc. This paper analyzes the influence mechanism of various factors on taxi drivers, establishes the decision-making model of taxi drivers, and designs the selection strategy.

(2) collect the data of a domestic airport and related taxis, give the taxi driver's decision-making scheme in this situation, and analyze the rationality of the decision-making model built in the previous question, as well as the dependence on various factors.

(3) in the loading area, it is usually the taxi queuing to carry passengers or the passenger queuing for taxis. Now, there are two parallel lanes in the loading area. It is necessary to design the scheduling scheme of the taxi and the passenger and set the loading point so as to make the loading efficiency of the loading area the highest.

(4) there are short-distance passengers and long-distance passengers in the airport. Taxi drivers can't refuse to take them, but they can take them back and forth. In order to balance the income of all taxis, it is necessary to design a priority scheme for short-distance vehicles and verify the scheme works.